Public Gender Egalitarianism: A Dataset of Dynamic Comparative Public Opinion Toward Egalitarian Gender Roles in the Public Sphere

### 2021-01-05 paper/dcpo_gender_roles.Rmd
revise description of using uncertainty per this @lallemang comment https://github.com/fsolt/dcpo_gender_roles/issues/18#issuecomment-754288959; clean up bibtex per this @byngdeuk comment https://github.com/fsolt/dcpo_gender_roles/issues/18#issuecomment-754095097

One aspect of latent-variable estimates of public opinion like the PGE dataset that is easy for researchers to overlook is the uncertainty in the estimates.
But neglecting to incorporate this uncertainty by using only the mean estimate for each country-year---that is, for example, the mean of the PGE scores---in an analysis can lead one to mistakenly conclude that the analysis supports the hypothesis [see @Tai2021] as well as to mistakenly conclude that it does _not_ support the hypothesis [see @Crabtree2015].
Therefore, taking the uncertainty in the PGE scores into account (e.g., via the \texttt{purrr} package [@Henry2019] in R or the \texttt{mi estimate:} command prefix in Stata) is crucial to reaching well-grounded conclusions.

>>>>

One aspect of latent-variable estimates of public opinion like the PGE dataset that is easy for researchers to overlook is the quantified uncertainty in the estimates.
But neglecting to incorporate this uncertainty by using only the mean estimate for each country-year in an analysis can lead one to mistakenly conclude that the analysis supports the hypothesis [see @Tai2021] as well as to mistakenly conclude that it does _not_ support the hypothesis [see @Crabtree2015].
Therefore, taking the uncertainty in the PGE scores into account is crucial to reaching well-grounded conclusions.
Step-by-step instructions for doing this via simulations, with examples, are included in the data download.
